---
title: "Applied Project"
output: html_document
date: "2023-04-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

```{r}
pacman::p_load(tidyverse)
library(tidyverse)
```


# Test dataset (not necessary to run!)
```{r}
roomie_data <- read.csv("Data-Correccted.csv")
roomie_data$Z001_03 <- tolower(roomie_data$Z001_03)

roomie1 <- roomie_data[which(roomie_data$Z001_03 == "paraply03"),]
roomie2 <- roomie_data[which(roomie_data$Z001_03 == "banan02"),]
roomie3 <- roomie_data[which(roomie_data$Z001_03 == "kage3"),]
roomie4 <- roomie_data[which(roomie_data$Z001_03 == "jordbær4"),]

roomie3 <- subset(roomie3, select = -c(QUESTNNR,MODE,STARTED,FINISHED,Q_VIEWER,LASTPAGE,MAXPAGE,MISSING,MISSREL,TIME_RSI,DEG_TIME))

roomie4 <- subset(roomie4, select = -c(QUESTNNR,MODE,STARTED,FINISHED,Q_VIEWER,LASTPAGE,MAXPAGE,MISSING,MISSREL,TIME_RSI,DEG_TIME))

roomie_data <- subset(roomie_data, select = -c(QUESTNNR,MODE,STARTED,FINISHED,Q_VIEWER,LASTPAGE,MAXPAGE,MISSING,MISSREL,TIME_RSI,DEG_TIME))

```
# Functions
## Old function (gives too low results)
DONT RUN!!!!
```{r}
euclid2 <- function(a) {

  pers_1_df <- data.frame()
  person_routine <- numeric(nrow(a)-1)
  cleanliness <- numeric(nrow(a)-1)
  communal_life <- numeric(nrow(a)-1)
  social_life <- numeric(nrow(a)-1)
  communication <- numeric(nrow(a)-1)
  person_nr <- numeric(nrow(a)-1)

  for (i in 2:nrow(a)) {
    person_routine[i-1] <- sqrt(sum((a[1,2:8]-a[i,2:8])^2))
    cleanliness[i-1] <- sqrt(sum((a[1,9:15]-a[i,9:15])^2))
    communal_life[i-1] <- sqrt(sum((a[1,16:18]-a[i,16:18])^2))
    social_life[i-1] <- sqrt(sum((a[1,19:25]-a[i,19:25])^2))
    communication[i-1] <- sqrt(sum((a[1,26:28]-a[i,26:28])^2))
    person_nr[i-1] <- a[i,1]
  }
  
  pers_1_df <- data.frame(person_nr,person_routine,cleanliness,communal_life,social_life,communication)
  return(pers_1_df)
}



```

## New and improved function (Final function maybe?)
```{r}
euclidv2 <- function(a) {
  n_cols <- 36  # number of columns to compute distances for
  
  # create empty data frame to store results
  pers_df <- data.frame(matrix(nrow = nrow(a) - 1, ncol = n_cols + 1))
  
  # name the columns of the data frame
  colnames(pers_df) <- c("person_nr", paste0("dist_", 1:n_cols))
  
  # iterate through each column and compute distances for each person
  for (j in 2:37) {
    if (j > n_cols + 1) break  # exit the loop if we've computed all the columns
    dist_vec <- numeric(nrow(a) - 1)
    for (i in 2:nrow(a)) {
      dist_vec[i-1] <- sqrt(sum((a[1,j]-a[i,j])^2))
    }
    pers_df[, j] <- dist_vec  # subtract 1 to match the column index
  }
  
  # add person number column to data frame
  pers_df$person_nr <- a[1, 1]
  
  return(pers_df)
}

```

## Function to calculate percentage of compatibility 
```{r}
# Define your function
percent <- function(x) {
  # convert input to recciprocal data
  result <- 1/(1+x)
  return(result)
}

```

## Function that summarizes the percentage data into categories 
```{r}
# Define function to summarize reciprocal data into categories
percent2 <- function(a) {
  # Take the mean of each category
  person_routine <- apply(a[, 33:36], 1, mean)
  cleanliness <- apply(a[, 1:7], 1, mean)
  communal_life <- apply(a[, 8:14], 1, mean)
  social_life <- apply(a[, 15:17], 1, mean)
  communication <- apply(a[, 18:23], 1, mean)
  #Create a new data frame with the summarized percentage values. 
  pers_1_df <- data.frame(person_routine, cleanliness, communal_life, social_life, communication)
  return(pers_1_df)
}

```

# Function for total similarity

1 = cleanliness
2 = communal life 
3 = social life
4 = communication
5 = personal routine
```{r}
# Defining function to calculate total similarity score based on weights and biases
total_sim <- function(a,b) {
  for (i in 1:nrow(a)) {
    # Saving un-weighted category percentages in variables
    cleanliness <- a[i,2]
    communal_life <- a[i,3]
    social_life <- a[i,4]
    communication <- a[i,5]
    personal_routine <- a[i,1]
  
    #Fectching categorical priority choices from survey
    first_pri <- b[1,29]
    second_pri <- b[1,30]
    third_pri <- b[1,31]
    fourth_pri <- b[1,32]
    fifth_pri <- b[1,33]
  
    # Redefining the first priority value to account for 40% of the total score
    if (first_pri == 1) {
      cleanliness <- cleanliness*40
      } else if (first_pri == 2) {
      communal_life <- communal_life*40
      } else if (first_pri == 3) {
      social_life <- social_life*40
      } else if (first_pri == 4) {
      communication <- communication*40
      } else if (first_pri == 5) {
      personal_routine <- personal_routine*40
      } 
  
    # Redefining the second priority value to account for 30% of the total score
    if (second_pri == 1) {
      cleanliness <- cleanliness*30
      } else if (second_pri == 2) {
      communal_life <- communal_life*30
      } else if (second_pri == 3) {
      social_life <- social_life*30
      } else if (second_pri == 4) {
      communication <- communication*30
      } else if (second_pri == 5) {
      personal_routine <- personal_routine*30
      } 

    # Redefining the third priority value to account for 15% of the total score
     if (third_pri == 1) {
      cleanliness <- cleanliness*15
      } else if (third_pri == 2) {
      communal_life <- communal_life*15
      } else if (third_pri == 3) {
      social_life <- social_life*15
      } else if (third_pri == 4) {
      communication <- communication*15
      } else if (third_pri == 5) {
      personal_routine <- personal_routine*15
      } 
  
    # Redefining the fourth priority value to account for 10% of the total score
    if (fourth_pri == 1) {
      cleanliness <- cleanliness*10
      } else if (fourth_pri == 2) {
      communal_life <- communal_life*10
      } else if (fourth_pri == 3) {
      social_life <- social_life*10
      } else if (fourth_pri == 4) {
      communication <- communication*10
      } else if (fourth_pri == 5) {
      personal_routine <- personal_routine*10
      } 
  
    # Redefining the fifth priority value to account for 5% of the total score
    if (fifth_pri == 1) {
      cleanliness <- cleanliness*5
      } else if (fifth_pri == 2) {
      communal_life <- communal_life*5
      } else if (fifth_pri == 3) {
      social_life <- social_life*5
      } else if (fifth_pri == 4) {
      communication <- communication*5
      } else if (fifth_pri == 5) {
      personal_routine <- personal_routine*5
      } 
  
      # summing all values together and dividing by 100 to get percentage value
      total_score <- (sum(cleanliness, communal_life, social_life, communication,
                    personal_routine))/100
    print(total_score)
  }
}
```


# Survey data
```{r}
#loading in data from public survey
roomie_experiment_data <- read.csv("data_test.csv")

#removing unnecessary columns from dataframe
roomie_experiment_data <- subset(roomie_experiment_data, select = -c(QUESTNNR,MODE,STARTED,FINISHED,Q_VIEWER,LASTPAGE,MAXPAGE,MISSING,MISSREL,TIME_RSI,DEG_TIME,SERIAL,REF))

#lower casing the code word chosen
roomie_experiment_data$Z001_03 <- tolower(roomie_experiment_data$Z001_03)
# remove rows with NA values
roomie_experiment_data <- na.omit(roomie_experiment_data)
# remove rows with negative values
roomie_experiment_data <- subset(roomie_experiment_data, A401>0)
# trim leading and trailing spaces and overwrite original variable
roomie_experiment_data$Z001_03 <- trimws(roomie_experiment_data$Z001_03)


#splitting up data table into roomie groups
roomie1 <- roomie_experiment_data[(roomie_experiment_data$Z001_03 == "paraply05"),]
roomie2 <- roomie_experiment_data[which(roomie_experiment_data$Z001_03 == "newage75"),]
roomie3 <- roomie_experiment_data[which(roomie_experiment_data$Z001_03 == "gulerod"),]
roomie4 <- roomie_experiment_data[which(roomie_experiment_data$Z001_03 == "longisland"),]
roomie5 <- roomie_experiment_data[which(roomie_experiment_data$Z001_03 == "rapand"),]
```






# Data analysis
## Apartment 1
```{r}
# Runging all necessary functions on roomie group 1
v2result1 <- euclidv2(roomie1)
v2percent1 <- percent(v2result1[,2:37])
v2cat_percent1 <- percent2(v2percent1)
total_sim(v2cat_percent1,roomie1)
```

## Apartment 2
```{r}

# Runging all necessary functions on roomie group 2
v2result2 <- euclidv2(roomie2)
v2percent2 <- percent(v2result2[,2:37])
v2cat_percent2 <- percent2(v2percent2)
total_sim(v2cat_percent2,roomie2)
```
## Apartment 3
```{r}

# Runging all necessary functions on roomie group 3
v2result3 <- euclidv2(roomie3)
v2percent3 <- percent(v2result3[1,2:37])
v2cat_percent3 <- percent2(v2percent3)
total_sim(v2cat_percent3,roomie3)
```
## Apartment 4
```{r}
# Runging all necessary functions on roomie group 4
v2result4 <- euclidv2(roomie4)
v2percent4 <- percent(v2result4[1,2:37])
v2cat_percent4 <- percent2(v2percent4)
total_sim(v2cat_percent4,roomie4)
```
## Apartment 5
```{r}
# Runging all necessary functions on roomie group 5
v2result5 <- euclidv2(roomie5)
v2percent5 <- percent(v2result5[1,2:37])
v2cat_percent5 <- percent2(v2percent5)
total_sim(v2cat_percent5,roomie5)
```


# Code used that we first tried but didnt give the results we wanted
```{r}
#apartment 1
percent_person_routine1 <- 1/(1+result_roomie1$person_routine)
percent_cleanliness1 <- 1/(1+result_roomie1$cleanliness)
percent_communal_life1 <- 1/(1+result_roomie1$communal_life)
percent_social_life1 <- 1/(1+result_roomie1$social_life)
percent_commmunication1 <- 1/(1+result_roomie1$communication)

percent_df1 <- data.frame(percent_person_routine1, percent_cleanliness1, percent_communal_life1, percent_social_life1, percent_commmunication1)
print(percent_df1)

# apartment 2
percent_person_routine2 <- 1/(1+result_roomie2$person_routine)
percent_cleanliness2 <- 1/(1+result_roomie2$cleanliness)
percent_communal_life2 <- 1/(1+result_roomie2$communal_life)
percent_social_life2 <- 1/(1+result_roomie2$social_life)
percent_commmunication2 <- 1/(1+result_roomie2$communication)

percent_df2 <- data.frame(percent_person_routine2, percent_cleanliness2, percent_communal_life2, percent_social_life2, percent_commmunication2)
print(percent_df2)

#apartment 3
percent_person_routine3 <- 1/(1+result_roomie3$person_routine)
percent_cleanliness3 <- 1/(1+result_roomie3$cleanliness)
percent_communal_life3 <- 1/(1+result_roomie3$communal_life)
percent_social_life3 <- 1/(1+result_roomie3$social_life)
percent_commmunication3 <- 1/(1+result_roomie3$communication)

percent_df3 <- data.frame(percent_person_routine3, percent_cleanliness3, percent_communal_life3, percent_social_life3, percent_commmunication3)
print(percent_df3)

#apartment 4
percent_person_routine4 <- 1/(1+result_roomie4$person_routine)
percent_cleanliness4 <- 1/(1+result_roomie4$cleanliness)
percent_communal_life4 <- 1/(1+result_roomie4$communal_life)
percent_social_life4 <- 1/(1+result_roomie4$social_life)
percent_commmunication4 <- 1/(1+result_roomie4$communication)

percent_df4 <- data.frame(percent_person_routine4, percent_cleanliness4, percent_communal_life4, percent_social_life4, percent_commmunication4)
print(percent_df4)

#apartment 5
percent_person_routine5 <- 1/(1+result_roomie5$person_routine)
percent_cleanliness5 <- 1/(1+result_roomie5$cleanliness)
percent_communal_life5 <- 1/(1+result_roomie5$communal_life)
percent_social_life5 <- 1/(1+result_roomie5$social_life)
percent_commmunication5 <- 1/(1+result_roomie5$communication)

percent_df5 <- data.frame(percent_person_routine5, percent_cleanliness5, percent_communal_life5, percent_social_life5, percent_commmunication5)
print(percent_df5)
```


